%-------------------------
% Resume in Latex
% Author : Daniel Urbina
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Daniel Urbina} \\ \vspace{1pt}
    \small 201-519-3072 $|$ \href{mailto:x@x.com}{\underline{du35@njit.edu}} $|$ 
    \href{https://linkedin.com/in/...}{\underline{linkedin.com/in/danielburbina}} $|$
    \href{https://github.com/...}{\underline{github.com/danielxurbina}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {New Jersey Institute of Technology}{Newark, NJ}
      {Bachelor of Science in Computer Science}{Sept. 2022 -- May 2025}
    \resumeSubheading
      {Hudson County Community College}{Jersey City, NJ}
      {Associate's of Science in Computer Science}{Sept. 2019 -- Aug. 2022}
    \resumeSubheading
        {Flatiron School}{New York, NY}
        {Software Engineering Immersive: Full-stack Development}{Jan. 2020 - Jun 2020}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Sales Associate}{May. 2019 -- Feb 2020}
      {Yogibo}{Paramus, NJ}
      \resumeItemListStart
        \resumeItem{Joined Yogibo mid-sale cycle with no prior experience and quickly adapted to exceed sales goals, resulting in ranking as a top 10 company-wide salesperson}
        \resumeItem{Boosted sales by engaging customers, up-selling through suggestive techniques, and demonstrating expert product knowledge}
        \resumeItem{Surpassed monthly revenue goals for seven months in a row, earning the title of Best Sales Associate in 2019}
    \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{OnTopic} $|$ \emph{JavaScript, React, Node.js, Express.js, MongoDB}}{Jan 2023 -- Present}
          \resumeItemListStart
            \resumeItem{Developed a full-stack web application that allows users to access real-time news updates, engage in discussions, and contribute their perspectives.}
            \resumeItem{The backend was built with Node.js and Express.js, the frontend with React, and MongoDB as the database solution for efficient data store and retrieval.}
            \resumeItem{Integrated the HackerNews API to dynamically fetch and present curated news content.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{InstaPlay} $|$ \emph{JavaScript, React, Ruby on Rails, Active Storage, PostgreSQL}}{June 2020 -- Present}
          \resumeItemListStart
            \resumeItem{Developed a full-stack web application that allows users to interact and explore new music as well as upload their own music.}
            \resumeItem{The backend was created with Ruby on Rails and PostgreSQL, while the frontend was made with React.}
            \resumeItem{Integrated Active Storage in Ruby on Rails to handle MP3 and image file uploads, providing users with the ability to upload and manage files securely.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Locali} $|$ \emph{JavaScript, React, Ruby on Rails, PostgreSQL}}{May 2020 -- Present}
          \resumeItemListStart
            \resumeItem{Developed a full-stack web application that allows users to explore and create events.}
            \resumeItem{The backend was created with Ruby on Rails and PostgreSQL, while the frontend was made with React.}
            \resumeItem{Utilized Fast JSON API gem in the Rails backend to serialize data efficiently and optimize data transfer between server and client.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{AI Chatbot} $|$ \emph{IBM Watson, Natural Language Processing}}{September 2018 - December 2018}
          \resumeItemListStart
            \resumeItem{Collaborated with classmates to design and develop an AI-powered self-service solution for Hudson County Community College}
            \resumeItem{Utilized IBM Watson to create a natural language processing (NLP) system that provided students with personalized assistance and support}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, C/C++, JavaScript, HTML/CSS, SQL} \\
     \textbf{Frameworks}{: React, Node.js, Express.js, Ruby on Rails} \\
     \textbf{Developer Tools}{: Git, Docker, VS Code, Visual Studio, IntelliJ} \\
     \textbf{Libraries}{: pandas, NumPy, Matplotlib, ActiveStorage}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
